### 2024-09-08 actuarial.qmd
20270907 - citations in block quotes

> "If a sociologist were predicting whether Professor X would go to the movies on a certain night, he might have an equation involving age, academic specialty, and introversion score.
> The equation might yield a probability of .90 that Professor X goes to the movie tonight.
> But if the family doctor announced that Professor X had just broken his leg, no sensible sociologist would stick with the equation.
> Why didn't the factor of 'broken leg' appear in the formula?
> Because broken legs are very rare, and in the sociologist's entire sample of 500 criterion cases plus 250 cross-validating cases, he did not come upon a single instance of it.
> He uses the broken leg datum confidently, because 'broken leg' is a subclass of a larger class we may crudely denote as 'relatively immobilizing illness or injury,' and movie-attending is a subclass of a larger class of 'actions requiring moderate mobility.' "
> [@Meehl1957, p. 269–270]

>>>>

> If a sociologist were predicting whether Professor X would go to the movies on a certain night, he might have an equation involving age, academic specialty, and introversion score.
> The equation might yield a probability of .90 that Professor X goes to the movie tonight.
> But if the family doctor announced that Professor X had just broken his leg, no sensible sociologist would stick with the equation.
> Why didn't the factor of 'broken leg' appear in the formula?
> Because broken legs are very rare, and in the sociologist's entire sample of 500 criterion cases plus 250 cross-validating cases, he did not come upon a single instance of it.
> He uses the broken leg datum confidently, because 'broken leg' is a subclass of a larger class we may crudely denote as 'relatively immobilizing illness or injury,' and movie-attending is a subclass of a larger class of 'actions requiring moderate mobility.'
> 
> --- Meehl [-@Meehl1957, p. 269–270]
